Lineage Analysis of CRISPR and shRNA Screens

### 2018-09-06 lineages_18Q3.Rmd

## Functions {.tabset .tabset-fade .tabset-pills}

### Significance thresholding

@@

### Make CRISPR grobs

@@

  # Mutation status
  crispr_color <- as.character(gene$Color)
  names(crispr_color) <- gene$Mutation_Status
  sig <- filter(crispr_signif, Hugo_Symbol == g)
  plot_mut <- ggplot(data = gene, aes(x = Mutation_Status, y = Score, color = Mutation_Status)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(alpha = 0.3, size = 0.7, position = position_jitter(w = 0.05)) +
    scale_color_manual(values = crispr_color) +
    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
    theme_light() +
    theme(legend.position = "none") +
    labs(x = paste0(g, " Mutation Status"), y = "CERES Score",
         title = "Mutation Status",
         subtitle = paste0("Wilcoxon test:\n- BH-corrected p-value: ", sig$p.adj.short, "\n- Uncorrected p-value: ", sig$p.short))

@@

### Make lineage plot

```{r}
makeCRISPRlinplot <- function(g) {
  sig <- filter(crispr_signif_lineage, Hugo_Symbol == g)
  if(nrow(sig) == 0) {
    return(NULL)
  }
  else {
    gene <- filter(crispr_data, Hugo_Symbol == g)
    gene <- merge(gene, sig, by = c("Hugo_Symbol", "lineage_name"))
    gene <- mutate(gene, lineage_name = reorder(lineage_name, p, mean))
    crispr_color <- as.character(gene$Color)
    names(crispr_color) <- gene$Mutation_Status
    score_range <- abs(range(gene$Score)[2] - range(gene$Score)[1])
    round_accuracy <- ifelse(score_range <= 2, 0.25,
                             ifelse(score_range <= 3, 0.5, 1.0))

    plot <- ggplot(data = gene, aes(x = lineage_name, y = Score)) +
      geom_point(alpha = 0.5, mapping = aes(color = Mutation_Status)) +
      scale_color_manual(values = crispr_color) +
      coord_cartesian(y = c(min(gene$Score), round_any(x = max(gene$Score), accuracy = round_accuracy, f = ceiling))) +
      geom_signif(data = gene, mapping = aes(xmin = lineage_name, xmax = lineage_name, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
      theme(legend.position = "top", axis.text.x = element_text(angle = 70, hjust = 1, size = 10)) +
      labs(y = "CERES Score",
           x = "Lineage",
           color = "Mutation Status",
           title = paste0(g, ": CERES score by cell line lineage"),
           subtitle = "Lineages sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.")
    return(plot)
  }
}
```

### Make tissue plot

@@

    plot <- ggplot(data = gene, aes(x = primary_tissue, y = Score)) +
      geom_point(alpha = 0.5, mapping = aes(color = Mutation_Status)) +
      scale_color_manual(values = crispr_color) +
      coord_cartesian(y = c(min(gene$Score), round_any(x = max(gene$Score), accuracy = round_accuracy, f = ceiling))) +
      geom_signif(data = gene, mapping = aes(xmin = primary_tissue, xmax = primary_tissue, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
      theme(legend.position = "top", axis.text.x = element_text(angle = 70, hjust = 1, size = 10)) +
      labs(y = "CERES Score",
           x = "Primary Tissue",
           color = "Mutation Status",
           title = paste0(g, ": CERES score by cell line primary tissue"),
           subtitle = "Primary tissues sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.")
    return(plot)
  }
}
```

## Cell line converter

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"
```

## Cell line metadata

@@

crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
colnames(crispr_meta)[7] <- "CCLE_Name"

shrna_meta <- read.delim("./data_munging/sample_info_18Q3_shrna.csv", sep = ",", header = TRUE, na.strings = c("", NA))
colnames(shrna_meta)[1] <- "CCLE_Name"
```

```{r}
dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)

test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
```

## Cancer Gene Census (CGC) gene list

@@

## MAF file

@@

# Select columns
maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Tumor_Sample_Barcode", "Broad_ID", "Variant_Classification", "isDeleterious"))
colnames(maf_df)[colnames(maf_df) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
# Add Mutation_Status column
maf_df$Mutation_Status <- ifelse(maf_df$Variant_Classification == "Missense_Mutation" | maf_df$isDeleterious == TRUE, "Mutant", "Other")
maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status")))

@@

## Copy number file

@@

## Gene expression file

@@

## CRISPR dependency probabilities

@@

## CRISPR data and annotations

@@

## shRNA data and annotations

```{r}
shrna_data <- readRDS("./../crispr_lineages_giant_files/shrna_data_18Q3.rds")
shrna_ccl <- data.frame("Broad_ID" = shrna_data$Broad_ID)
```

```{r, eval=FALSE}
write(union(as.character(distinct(crispr_data[which(is.na(crispr_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name), as.character(distinct(shrna_data[which(is.na(shrna_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name)), file = "./data_munging//na_ccl_in_converter.txt")
```

# Exploration

```{r fig.height=8, fig.width=12}
ggsave(filename = "./plots_18Q3/crispr/score_mut_summ.pdf", plot = grid.draw(rbind(ggplotGrob(maf_ccl_annot_plot), ggplotGrob(score_summ_plot), size = "first")), width = 12, height = 8, device = "pdf")
```

@@

## CRISPR

```{r, eval=FALSE}
crispr_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif <- adj_signif(crispr_signif)
crispr_signif <- crispr_signif[order(crispr_signif$p),]
saveRDS(crispr_signif, "./data_munging/rds/crispr_signif.rds")

@@

knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_gene_plot <- ggplot(data = crispr_signif) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3",), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  coord_cartesian(ylim = c(0, 4500)) +
  scale_y_continuous(breaks = seq(0, 4500, by = 500), labels = formatC(seq(0, 4500, by = 500), format = "d")) +
  #stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_gene_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
```

```{r, eval=FALSE}
crispr_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_lineage <- adj_signif(crispr_signif_lineage)
crispr_signif_lineage <- crispr_signif_lineage[order(crispr_signif_lineage$p),]
saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_lineage.rds")

@@

knitr::kable(filter(crispr_signif_lineage, p < 0.05)[, c("Hugo_Symbol", "lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

### Grouped by gene and tissue

```{r, eval=FALSE}
crispr_signif_tissue <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_tissue.rds")

@@

knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines by Primary Tissue, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_gene_tissue_plot <- ggplot(data = crispr_signif_tissue) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3",), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  scale_y_continuous(breaks = seq(0, 50000, by = 5000), labels = formatC(seq(0, 50000, by = 5000), format = "d")) +
  #stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_gene_tissue_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_gene_tissue_plot, width = 8, height = 4, device = "pdf")
```

## shRNA

>>>>

# Functions {.tabset .tabset-fade .tabset-pills}

## Significance thresholding

@@

## Make CRISPR grobs

@@

  # Mutation status
  crispr_color <- as.character(gene$Color)
  names(crispr_color) <- gene$Mutation_Status
  sig <- filter(crispr_signif, Hugo_Symbol == g)
  plot_mut <- ggplot(data = gene, aes(x = Mutation_Status, y = Score, color = Mutation_Status)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(alpha = 0.3, size = 0.7, position = position_jitter(w = 0.05)) +
    scale_color_manual(values = crispr_color) +
    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
    theme_light() +
    theme(legend.position = "none") +
    labs(x = paste0(g, " Mutation Status"), y = "CERES Score",
         title = "Mutation Status",
         subtitle = paste0("Wilcoxon test:\n- BH-corrected p-value: ", sig$p.adj.short, "\n- Uncorrected p-value: ", sig$p.short, "\nMutant lines harbor deleterious mutations."))

@@

## Make lineage plot

```{r}
makeCRISPRlinplot <- function(g) {
  sig <- filter(crispr_signif_lineage, Hugo_Symbol == g)
  if(nrow(sig) == 0) {
    return(NULL)
  }
  else {
    gene <- filter(crispr_data, Hugo_Symbol == g)
    gene <- merge(gene, sig, by = c("Hugo_Symbol", "group_general_lineage_name"))
    gene <- mutate(gene, group_general_lineage_name = reorder(group_general_lineage_name, p, mean))
    crispr_color <- as.character(gene$Color)
    names(crispr_color) <- gene$Mutation_Status
    score_range <- abs(range(gene$Score)[2] - range(gene$Score)[1])
    round_accuracy <- ifelse(score_range <= 2, 0.25,
                             ifelse(score_range <= 3, 0.5, 1.0))

    plot <- ggplot(data = gene, aes(x = group_general_lineage_name, y = Score)) +
      geom_point(alpha = 0.5, mapping = aes(color = Mutation_Status)) +
      scale_color_manual(values = crispr_color) +
      coord_cartesian(y = c(min(gene$Score), round_any(x = max(gene$Score), accuracy = round_accuracy, f = ceiling))) +
      geom_signif(data = gene, mapping = aes(xmin = group_general_lineage_name, xmax = group_general_lineage_name, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
      theme(legend.position = "top", axis.text.x = element_text(angle = 70, hjust = 1, size = 10)) +
      labs(y = "CERES Score",
           x = "Lineage",
           color = "Mutation Status",
           title = paste0(g, ": CERES score by cell line lineage"),
           subtitle = "Lineages sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.\nMutant lines harbor deleterious mutations.")
    return(plot)
  }
}
```

## Make tissue plot

@@

    plot <- ggplot(data = gene, aes(x = primary_tissue, y = Score)) +
      geom_point(alpha = 0.5, mapping = aes(color = Mutation_Status)) +
      scale_color_manual(values = crispr_color) +
      coord_cartesian(y = c(min(gene$Score), round_any(x = max(gene$Score), accuracy = round_accuracy, f = ceiling))) +
      geom_signif(data = gene, mapping = aes(xmin = primary_tissue, xmax = primary_tissue, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
      theme(legend.position = "top", axis.text.x = element_text(angle = 70, hjust = 1, size = 10)) +
      labs(y = "CERES Score",
           x = "Primary Tissue",
           color = "Mutation Status",
           title = paste0(g, ": CERES score by cell line primary tissue"),
           subtitle = "Primary tissues sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.\nMutant lines harbor deleterious mutations.")
    return(plot)
  }
}
```

# Data management

## D. Charytonowicz ell line converter

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"
```

```{r}
ccl_converter_test <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", header = TRUE)
colnames(ccl_converter_test)[colnames(ccl_converter_test) == "ccle_cell_line_name"] <- "CCLE_Name"
colnames(ccl_converter_test)[colnames(ccl_converter_test) == "broad_id"] <- "Broad_ID"
```

## DepMap cell line metadata

@@

# From figshare
crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
colnames(crispr_meta)[7] <- "CCLE_Name"
```

```{r, include=FALSE}
dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
old_dan_test <- select(ccl_converter_test, CCLE_Name, Broad_ID, cell_line_name)
old_dan_test <- old_dan_test[-which(old_dan_test$CCLE_Name == ""), ]
colnames(old_dan_test)[colnames(old_dan_test) == "Broad_ID"] <- "Broad_ID_Old"
ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)

test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
test <- merge(test, old_dan_test, by = "CCLE_Name", all = TRUE)
test$BroadIDs_match_Daniel <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
test$BroadIDs_match_Old <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Old), TRUE, FALSE)

test_false_Daniel <- filter(test, BroadIDs_match_Daniel == FALSE)
test_false_Old <- filter(test, BroadIDs_match_Old == FALSE)
# write.table(test_false, file = "~/Desktop/cell_line_database_problems.csv", quote = FALSE, sep = ",")
```

## CGC gene list

@@

## CCLE MAF file

@@

# Select columns
maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Tumor_Sample_Barcode", "Broad_ID", "Variant_Classification", "isDeleterious"))
colnames(maf_df)[colnames(maf_df) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
# Add Mutation_Status column
maf_df$Mutation_Status <- ifelse(maf_df$isDeleterious == TRUE, "Mutant", "Other")
maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status", "Mutation_Status_Nonsilent")))

@@

## CCLE copy number file

@@

## CCLE gene expression file

@@

## DepMap dependency probabilities

@@

## Merge CRISPR data and annotations

@@

@@

## Grouped by gene

### Deleterious vs. Other

```{r, eval=TRUE}
crispr_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif <- adj_signif(crispr_signif)
crispr_signif <- crispr_signif[order(crispr_signif$p),]
saveRDS(crispr_signif, "./data_munging/rds/crispr_signif.rds")

@@

knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_gene_plot <- ggplot(data = crispr_signif) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  coord_cartesian(ylim = c(0, 3500)) +
  scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_gene_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
```

### Non-silent mutant vs. Other

```{r, eval=TRUE}
crispr_signif_nonsilent<- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_nonsilent <- adj_signif(crispr_signif_nonsilent)
crispr_signif_nonsilent <- crispr_signif_nonsilent[order(crispr_signif_nonsilent$p),]
saveRDS(crispr_signif_nonsilent, "./data_munging/rds/crispr_signif_nonsilent.rds")

write.table(crispr_signif_nonsilent, file = "~/Desktop/crispr_signif_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_nonsilent <- readRDS("./data_munging/rds/crispr_signif_nonsilent.rds")

knitr::kable(filter(crispr_signif_nonsilent, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_gene_nonsilent_plot <- ggplot(data = crispr_signif_nonsilent) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  # coord_cartesian(ylim = c(0, 3500)) +
  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_gene_nonsilent_plot
```

## Grouped by gene and lineage

### Deleterious vs. Other

```{r, eval=TRUE}
crispr_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_lineage <- adj_signif(crispr_signif_lineage)
crispr_signif_lineage <- crispr_signif_lineage[order(crispr_signif_lineage$p),]
saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_lineage.rds")

@@

knitr::kable(filter(crispr_signif_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_lineage_plot <- ggplot(data = crispr_signif_lineage) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  # coord_cartesian(ylim = c(0, 3500)) +
  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_lineage_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
```

### Non-silent mutant vs. Other

```{r, eval=TRUE}
crispr_signif_nonsilent_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_nonsilent_lineage <- adj_signif(crispr_signif_nonsilent_lineage)
crispr_signif_nonsilent_lineage <- crispr_signif_nonsilent_lineage[order(crispr_signif_nonsilent_lineage$p),]
saveRDS(crispr_signif_nonsilent_lineage, "./data_munging/rds/crispr_signif_nonsilent_lineage.rds")

write.table(crispr_signif_nonsilent_lineage, file = "~/Desktop/crispr_signif_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_nonsilent_lineage.rds")

knitr::kable(filter(crispr_signif_nonsilent_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_lineage_nonsilent_plot <- ggplot(data = crispr_signif_nonsilent_lineage) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  # coord_cartesian(ylim = c(0, 3500)) +
  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_lineage_nonsilent_plot
```

## Grouped by gene and tissue

### Deleterious vs. Other

```{r, eval=TRUE}
crispr_signif_tissue <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_tissue.rds")

@@

knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_tissue_plot <- ggplot(data = crispr_signif_tissue) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  # scale_y_continuous(breaks = seq(0, 50000, by = 5000), labels = formatC(seq(0, 50000, by = 5000), format = "d")) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_tissue_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_tissue_plot, width = 8, height = 4, device = "pdf")
```

### Non-silent mutant vs. Other

```{r, eval=TRUE}
crispr_signif_nonsilent_tissue <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_nonsilent_tissue <- adj_signif(crispr_signif_nonsilent_tissue)
crispr_signif_nonsilent_tissue <- crispr_signif_nonsilent_tissue[order(crispr_signif_nonsilent_tissue$p),]
saveRDS(crispr_signif_nonsilent_tissue, "./data_munging/rds/crispr_signif_nonsilent_tissue.rds")

write.table(crispr_signif_nonsilent_tissue, file = "~/Desktop/crispr_signif_nonsilent_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_nonsilent_tissue <- readRDS("./data_munging/rds/crispr_signif_nonsilent_tissue.rds")
